Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
Fixing sentence in the introduction, consistent use of GOURMAND

While it is interesting to make problems harder and invent better planning
algorithms to solve those probabilistic complex problems, one must not forget
if the problem makes sense in the real world.

>>>>

While it is interesting to make problems harder and invent better planning
algorithms to solve those probabilistic complex problems, we evaluate whether
or not these problems are coherent with real-world situations.
